---
title: 'Supplement extracted data with more data'
author: "Stylianos Serghiou"
date: '`r format(Sys.time(), "%d/%m/%Y")`'
output:
  prettydoc::html_pretty:
    # no code_folding available
    theme: hpstr      # or: architect; https://github.com/yixuan/prettydoc
    highlight: github # or: vignette
    toc: TRUE         # no toc_float available
    df_print: kable   # obviates %>% kable; does not replace styling though
  tufte::tufte_handout: default
  pdf_document:
    highlight: tango
    df_print: kable
    latex_engine: pdflatex
    keep_tex: yes
  rmdformats::readthedown:
    highlight: kate
    df_print: kable    # obviates %>% kable; does not replace styling though
    code_folding: hide # or: show; (comment out to not give option)
  tufte::tufte_html: 
    toc: TRUE
  epuRate::epurate:
    df_print: kable
    toc: yes
  html_document:
    highlight: tango
    theme: sandstone
    df_print: kable
    toc: yes
    toc_depth: 2
    toc_float: yes
    css: "path_to_custom.css"
header-includes:
- \DeclareUnicodeCharacter{3B8}{~}
- \DeclareUnicodeCharacter{3B1}{~}
- \DeclareUnicodeCharacter{3B2}{~}
- \DeclareUnicodeCharacter{223C}{~}
- \DeclareUnicodeCharacter{2264}{~}
- \DeclareUnicodeCharacter{2265}{~}
- \DeclareUnicodeCharacter{2581}{~}
- \DeclareUnicodeCharacter{2582}{~}
- \DeclareUnicodeCharacter{2583}{~}
- \DeclareUnicodeCharacter{2585}{~}
- \DeclareUnicodeCharacter{2586}{~}
- \DeclareUnicodeCharacter{2587}{~} 
- \DeclareUnicodeCharacter{FB00}{~} 
- \usepackage{graphicx}
editor_options: 
  chunk_output_type: inline
---

<style>
p {

text-align: justify;
text-justify: interword;
padding: 0 0 0.5em 0

}
</style>

```{r, echo=FALSE}
# Load packages
library(knitr)
library(rmdformats)
library(kableExtra)
library(ggplot2)
library(magrittr)



######### knitr

# Define chunk options
opts_chunk$set(echo = TRUE
               , cache     = FALSE      # if TRUE, no need to rerun chunks
               #, cache.lazy = TRUE     # use when have big objects (>1 GB)
               , cache.comments = FALSE # do not rebuild if comments change
               , tidy      = FALSE      # can play with this
               , warning   = FALSE 
               , message   = FALSE
               , comment   = NA
               , fig.align = "center"
               , fig.width = 7
               # , fig.path  = "Figs/" # export all figures to dir Figs
               , linewidth = 91)

opts_knit$set(width = 75)

# Initiatialize hook
hook_output = knit_hooks$get("output")

# Hook to wrap output text when it exceeds 'n' using linewidth
knit_hooks$set(output = function(x, options) {
  
  if (!is.null(n <- options$linewidth)) {
    x = knitr:::split_lines(x)
    
    # wrap lines wider than 'n' 
    if (any(nchar(x) > n)) 
      x <- strwrap(x, width = n)
      x <- paste(x, collapse = "\n")
  }
  hook_output(x, options)
})

# For more knitr options visit: https://yihui.name/knitr/options/
# and his github page: https://github.com/yihui/knitr-examples



######### kableExtra

options(knitr.kable.NA = ''  # replace NAs in tables with blank
        , digits = 3)          # round digits (doesn't work without this here!)

## Example use
# data.frame(x = c(1,2,3), y = c(4,5,6), z = c(7,8,9)) %>% 
#   kable(booktabs = T) %>% kable_styling()

# Function to simplify table styling
sable <- function(tab, escape = T, full_width = F, drop = F, font_size = 12) {
  if (drop) {
    tab %>%
      kable(escape = escape, booktabs = T) %>%
      collapse_rows(valign = "top") %>% 
      kable_styling("striped", 
                    position = "center", 
                    full_width = full_width, 
                    font_size = font_size)
  } else {
    tab %>%
      kable(escape = escape, booktabs = T) %>%
      kable_styling("striped", 
                    position = "center", 
                    full_width = full_width,
                    font_size = font_size)
  }
}

## Guidelines
# No longer need to define options(knitr.table.format = "html"). It is now automatically done as soon as you load kableExtra
# No need to run kable() every time - done automatically as soon as you load kableExtra
# Loading kableExtra nullifies any styling applied by df_table: kable in the preamble - if you are content with standard formatting, DO NOT load kableExtra



#########  ggplot2

# Set up preferred theme in ggplot2
my_theme <- 
  # this and theme_minimal() are my favorite
  theme_light() +  
  theme(
    text  = element_text(color = "grey20"),
    title = element_text(face = "bold"),
    legend.key   = element_rect(colour = NA, fill = NA),  # Avoid borders
    axis.text.x  = element_text(margin = ggplot2::margin(b = 10)),
    axis.text.y  = element_text(margin = ggplot2::margin(l = 10))
  )

# Make the above theme the default theme
original_theme <- theme_set(my_theme)

# Use ggsave to save plots after plotting - this reduces size dramatically




######### Tabbed sections

# You can organize content using tabs by applying the .tabset class attribute to headers within a document. This will cause all sub-headers of the header with the .tabset attribute to appear within tabs rather than as standalone sections. For example:

## Quarterly Results {.tabset}

### By Product



######### Update package

# To update the package use:
# Replace ~/serghiouTemplates/inst/rmarkdown/templates/report/skeleton.rmd
# library(devtools); setwd("/Users/Stelios/"); install("serghiouTemplates")
```

# Objectives

Supplement already extracted data with the following data:

- Responsible party
- Study sponsor
- Collaborators
- Investigators
- Email address of investigator (if possible) 
- Dates of updated recruitment status 


***


# Setup

```{r}
# Load packages
library(clinicaltrialr)
library(furrr)
library(future)
library(magrittr)
library(pbapply)
library(readxl)
library(tidyverse)

# Import data
ct <- read_xlsx(
  "../../data/interim_data/clinicaltrials_non-vaccine_trials_all-records_.xlsx"
)
```


Create function to download trials.

```{r}
read_trials <- function(NCT) {
  
  NCT %>% 
    clinicaltrialr::ct_read_trial_xml() %>% 
    clinicaltrialr::ct_read_trial_csv()
  
}
```


Prepare multi-core process.

```{r}
future::plan(multiprocess, workers = 8)
```


***


# Download data

```{r, eval=FALSE}
# Download
new_ct <- 
  ct %$% 
  furrr::future_map_dfr(nct_id, read_trials)

# Save
write_csv(new_ct, "../../data/interim_data/ct-data_suppl_new-ct.csv")
```


***


# Join data

```{r}
new_ct %>% 
  select(
    responsible_party, 
    starts_with("study_spo"), 
    starts_with("coll"),
    starts_with("invest"), 
    last_update_posted_date,
    extraction_date
  ) %>% 
  bind_cols(ct, .) %>% 
  write_excel_csv("../../data/interim_data/ct-data_suppl_ct.csv")
```


***


# Save

```{r save}
# Save
save(list = ls(), file = "ct-data_suppl.RData")
```


***


# Documentation {.tabset}

## Session Info

```{r session_info, echo=FALSE}
print(sessionInfo(), locale = F)
```


## References

```{r refs, echo=FALSE}
(.packages()) %>% sort %>% lapply(citation) %>% lapply(c) %>% unique
```
