---
title: 'Pediatric clinical trials: Figures'
author: "Stylianos Serghiou"
date: '`r format(Sys.time(), "%d/%m/%Y")`'
output:
  prettydoc::html_pretty:
    # no code_folding available
    theme: hpstr      # or: architect; https://github.com/yixuan/prettydoc
    highlight: github # or: vignette
    toc: TRUE         # no toc_float available
    df_print: kable   # obviates %>% kable; does not replace styling though
  tufte::tufte_handout: default
  pdf_document:
    highlight: tango
    df_print: kable
    latex_engine: pdflatex
    keep_tex: yes
  rmdformats::readthedown:
    highlight: kate
    df_print: kable    # obviates %>% kable; does not replace styling though
    code_folding: hide # or: show; (comment out to not give option)
  tufte::tufte_html: 
    toc: TRUE
  epuRate::epurate:
    df_print: kable
    toc: yes
  html_document:
    highlight: tango
    theme: sandstone
    df_print: kable
    toc: yes
    toc_depth: 2
    toc_float: yes
    css: "path_to_custom.css"
header-includes:
- \DeclareUnicodeCharacter{3B8}{~}
- \DeclareUnicodeCharacter{3B1}{~}
- \DeclareUnicodeCharacter{3B2}{~}
- \DeclareUnicodeCharacter{223C}{~}
- \DeclareUnicodeCharacter{2264}{~}
- \DeclareUnicodeCharacter{2265}{~}
- \DeclareUnicodeCharacter{2581}{~}
- \DeclareUnicodeCharacter{2582}{~}
- \DeclareUnicodeCharacter{2583}{~}
- \DeclareUnicodeCharacter{2585}{~}
- \DeclareUnicodeCharacter{2586}{~}
- \DeclareUnicodeCharacter{2587}{~} 
- \DeclareUnicodeCharacter{FB00}{~} 
- \usepackage{graphicx}
editor_options: 
  chunk_output_type: inline
---

<style>
p {

text-align: justify;
text-justify: interword;
padding: 0 0 0.5em 0

}
</style>

```{r setup, include=FALSE}
# Load packages
library(knitr)
library(rmdformats)
library(kableExtra)
library(ggplot2)
library(magrittr)



######### knitr

# Define chunk options
opts_chunk$set(
  echo = T,
  cache = F,  # if TRUE, no need to rerun chunks
  # cache.lazy = TRUE,  # use with big objects (>1 GB)
  cache.comments = F,  # do not rebuild if comments change
  tidy = F,  # can play with this
  warning = F, 
  message = F,
  comment = NA,
  fig.align = "center",
  fig.width = 7,
  # fig.path = "Figs/",  # export all figures to dir Figs
  linewidth = 91,
  width = 75
)


# Initiatialize hook
hook_output = knit_hooks$get("output")


# Hook to wrap output text when it exceeds 'n' using linewidth
knit_hooks$set(output = function(x, options) {
  
  if (!is.null(n <- options$linewidth)) {
    x = knitr:::split_lines(x)
    
    # wrap lines wider than 'n' 
    if (any(nchar(x) > n)) 
      x <- strwrap(x, width = n)
      x <- paste(x, collapse = "\n")
  }
  hook_output(x, options)
})


# Times a chunk and prints the time it took to run it under the chunk
# To time a chunk, include in the chunk options: {r my_chunk, timeit=TRUE}
knitr::knit_hooks$set(timeit = local({
  now = NULL
  function(before, options) {
    if (before) {
      now <<- Sys.time()
    } else {
      res = difftime(Sys.time(), now)
      now <<- NULL
      # use options$label if you want the chunk label as well
      paste('Time for this code chunk:', as.character(res))
    }
  }})
)


# For more knitr options visit: https://yihui.name/knitr/options/
# and his github page: https://github.com/yihui/knitr-examples



######### kableExtra

options(knitr.kable.NA = ''  # replace NAs in tables with blank
        , digits = 3)          # round digits (doesn't work without this here!)

## Example use
# data.frame(x = c(1,2,3), y = c(4,5,6), z = c(7,8,9)) %>% 
#   kable(booktabs = T) %>% kable_styling()

# Function to simplify table styling
sable <- function(tab, escape = T, full_width = F, drop = F, font_size = 12) {
  if (drop) {
    tab %>%
      kable(escape = escape, booktabs = T) %>%
      collapse_rows(valign = "top") %>% 
      kable_styling("striped", 
                    position = "center", 
                    full_width = full_width, 
                    font_size = font_size)
  } else {
    tab %>%
      kable(escape = escape, booktabs = T) %>%
      kable_styling("striped", 
                    position = "center", 
                    full_width = full_width,
                    font_size = font_size)
  }
}

## Guidelines
# No longer need to define options(knitr.table.format = "html"). It is now automatically done as soon as you load kableExtra
# No need to run kable() every time - done automatically as soon as you load kableExtra
# Loading kableExtra nullifies any styling applied by df_table: kable in the preamble - if you are content with standard formatting, DO NOT load kableExtra



#########  ggplot2

# Set up preferred theme in ggplot2
my_theme <- 
  # this and theme_minimal() are my favorite
  theme_light() +  
  theme(
    axis.ticks = element_blank(),
    axis.title = element_text(face = "bold"),
    axis.text.x = element_text(margin = margin(t = 3)),
    axis.text.y  = element_text(margin = margin(r = 3)),
    legend.key = element_rect(colour = NA, fill = NA),  # Avoid borders
    panel.border = element_blank(), 
    text = element_text(color = "grey20"),
    title = element_text(face = "bold")
  )

# Make the above theme the default theme
original_theme <- theme_set(my_theme)

# Use ggsave to save plots after plotting - this reduces size dramatically



######### Live preview

# Preview the HTML without having to re-knit
# https://www.r-bloggers.com/create-r-markdown-reports-and-presentations-even-better-with-these-3-practical-tips/amp/

# xaringan::infinite_moon_reader()




######### Tabbed sections

# You can organize content using tabs by applying the .tabset class attribute to headers within a document. This will cause all sub-headers of the header with the .tabset attribute to appear within tabs rather than as standalone sections. For example:

## Quarterly Results {.tabset}

### By Product



######### Update package

# To update the package use:
# Replace ~/serghiouTemplates/inst/rmarkdown/templates/report/skeleton.rmd
# library(devtools); setwd("/Users/Stelios/"); install("serghiouTemplates")
```


# Setup {.tabset}

<!-- Chunk called setup_2 to avoid running it automatically -->

```{r setup_2}
# Load packages
library(magrittr)
library(tidyverse)  # load last to avoid masking by others
library(treemapify)


# Import data
trials <- read_csv("../../data/tidy_data/trials.csv")
who <- read_csv(
  "../../data/tidy_data/who.csv", col_types = cols(ID = col_character())
)
```


***


# Treemaps

## Create dataset

Number of eligible trials with categorizable conditions.

```{r}
trials %>% 
  count(is_eligible, is_classified, sort = T) %>% 
  sable()
```

Create dataset.

```{r}
# Only maintain up to level_four
treemaps <- 
  trials %>% 
  filter(is_eligible, is_classified) %>%
  select(nct_id, who_condition_ids, status_june23_sc, n_sample) %>% 
  separate_rows(who_condition_ids, sep = "; ") %>% 
  right_join(who, by = c("who_condition_ids" = "ID")) %>% 
  filter(!is.na(level_four) & is.na(level_five))

# Remaining trials
sprintf("Number of remaining trials = %s", nrow(treemaps))
```


```{r}
# Create dataset
treemaps %<>%
  group_by(level_two, level_three, level_four, relative_both_dalys) %>% 
  summarise(
    sample_size = sum(n_sample),
    n_complete_enroll = sum(str_detect(status_june23_sc, "C|E|R"), na.rm = T),
    p_complete_enroll = mean(str_detect(status_june23_sc, "C|E|R"), na.rm = T)
  ) %>% 
  mutate(complete_enroll = case_when(
    is.na(p_complete_enroll) | is.nan(p_complete_enroll)  ~ NA_character_,
    p_complete_enroll > 0.5 ~ ">50%",
    p_complete_enroll < 0.25 ~ "0-25%",
    T ~ "25-50%"
  )) %>%
  mutate(complete_enroll = factor(complete_enroll)) %>% 
  ungroup()

# Glimpse
glimpse(treemaps)
```


Count those that have completed enrolling or are actively enrolling.

```{r}
treemaps %>%
  count(complete_enroll) %>% 
  sable()
```

Identify levels with 0-50% enrollment.

```{r}
treemaps %>% 
  filter(complete_enroll %in% c("25-50%", "0-25%")) %>% 
  select(3:8) %>% 
  sable()
```


## Plot level_four

Using `treemapify` - same color across level_two, no complete_enroll.

```{r}
# Create palette
colfunc <- colorRampPalette(c("red", "yellow", "green"))

# Plot
treemaps %>%
  mutate_at(vars(sample_size), na_if, 0) %>% 
  ggplot(aes(
    area = relative_both_dalys, 
    fill = sample_size,
    label = level_four,
    subgroup = level_two,
    subgroup2 = level_three
  ), color = "white") +
  geom_treemap(color = "white", size = 1) +
  geom_treemap_text(
    colour = "grey20", 
    place = "centre", 
    grow = T, 
    reflow = T, 
    min.size = 1,
    padding.x = unit(2, units = "mm"),
    padding.y = unit(2, units = "mm"),
  ) +
  geom_treemap_subgroup_border(color = "white", size = 5) +
  geom_treemap_subgroup2_border(color = "white", size = 2) +
  labs(fill = "Total sample") +
  theme(legend.title = element_text(vjust = 2)) +
  scale_fill_gradient(
    low = "#F2DF91",
    high = "#CE0A04",
    na.value = "grey90",
    name = "Total sample",
    labels = scales::comma
  )
  # scale_fill_gradientn(
  #   labels = scales::comma,
  #   colours = heat.colors(10, alpha = 0.65),
  #   na.value = "grey50"
  # )
  # scale_fill_distiller(palette = "Greens")
  # scale_fill_distiller(palette = "Spectral")
  # scale_fill_gradientn(colours = alpha(colfunc(10), 0.7))
  # scale_fill_viridis_c(option = "B")
  # scale_fill_gradient(low = "yellow", high = "red", na.value = "grey")
  
# Save
ggsave("../../output/figure_output/figures_treemap_fill.jpg")
```


Using `treemapify` - different color across level_two, no complete_enroll.

```{r}
# Plot
treemaps %>%
  mutate_at(vars(sample_size), na_if, 0) %>% 
  ggplot(aes(
    area = relative_both_dalys, 
    fill = level_two,
    label = level_four,
    subgroup = level_two,
    subgroup2 = level_three
  ), color = "white") +
  geom_treemap(aes(alpha = sample_size), color = "white", size = 1) +
  geom_treemap_text(
    colour = "grey20", 
    place = "centre", 
    grow = T, 
    reflow = T,
    min.size = 1,
    padding.x = unit(1.5, units = "mm"),
    padding.y = unit(1.5, units = "mm"),
  ) +
  geom_treemap_subgroup_border(color = "white", size = 5) +
  geom_treemap_subgroup2_border(color = "white", size = 2) +
  scale_alpha(
    labels = scales::comma,
    range = c(0.35, 0.85), 
    name = "Total sample", 
    na.value = 0.1
  ) +
  scale_fill_discrete(guide = "none")

# Save
ggsave("../../output/figure_output/figures_treemap_alpha.jpg")
```


Using `treemapify` - same color across level_two, with complete_enroll.

```{r}
# Create palette
colfunc <- colorRampPalette(c("red", "yellow", "green"))

# Plot
treemaps %>%
  mutate_at(vars(sample_size), na_if, 0) %>% 
  ggplot(aes(
    area = relative_both_dalys, 
    fill = sample_size,
    label = level_four,
    subgroup = level_two,
    subgroup2 = level_three
  ), color = "white") +
  geom_treemap(color = "white", size = 1) +
  geom_treemap_text(
    aes(color = complete_enroll),
    place = "centre", 
    grow = T, 
    reflow = T, 
    min.size = 1,
    padding.x = unit(2, units = "mm"),
    padding.y = unit(2, units = "mm"),
    show.legend = T
  ) +
  geom_treemap_subgroup_border(color = "white", size = 5) +
  geom_treemap_subgroup2_border(color = "white", size = 2) +
  labs(color = "Complete or recruiting") +
  guides(color = guide_legend(override.aes = list(size = 3))) +
  theme(
    legend.title = element_text(vjust = 2)
  ) +
  scale_fill_gradient(
    low = "#F2DF91",
    high = "#CE0A04",
    na.value = "grey90",
    name = "Total sample",
    labels = scales::comma
  )
  # scale_fill_gradientn(
  #   labels = scales::comma,
  #   colours = heat.colors(10, alpha = 0.65),
  #   na.value = "grey50"
  # )
  # scale_fill_distiller(palette = "Greens")
  # scale_fill_distiller(palette = "Spectral")
  # scale_fill_gradientn(colours = alpha(colfunc(10), 0.7))
  # scale_fill_viridis_c(option = "B")
  # scale_fill_gradient(low = "yellow", high = "red", na.value = "grey")
  
# Save
ggsave("../../output/figure_output/figures_treemap_fill_status.jpg")
```


Using `treemap`.

```{r}
treemaps %>% 
  treemap::treemap(
    index = c("level_two", "level_three", "level_four"),
    vSize = "relative_both_dalys",
    vColor = "sample_size",
    type = "index"
  )
```


Using `ggraph`. This has not been implemented yet. To implement, see guides [here](https://www.data-imaginist.com/2017/ggraph-introduction-layouts/), [here](https://ggraph.data-imaginist.com/reference/geom_node_tile.html) and [here](https://www.data-imaginist.com/2017/introducing-tidygraph/).

```{r}
# Create directed graph
level_two <- 
  trials %>% 
  filter(is_eligible, is_condition_defined_in_who) %>%
  select(nct_id, who_condition_ids, n_sample) %>% 
  separate_rows(who_condition_ids, sep = "; ") %>% 
  right_join(who, by = c("who_condition_ids" = "ID")) %>% 
  filter(!is.na(level_two) & is.na(level_three)) %>%
  group_by(level_two, level_three, level_four, relative_both_dalys) %>% 
  summarise(sample_size = sum(n_sample, na.rm = T))
```


Alternative choices include [plotly](https://plotly.com/r/treemaps/) and [world clouds](https://cran.r-project.org/web/packages/wordcloud2/vignettes/wordcloud.html).


## Plot level_three

Create data.

```{r}
treemaps <- 
  trials %>% 
  filter(is_eligible, is_condition_defined_in_who) %>%
  select(nct_id, who_condition_ids, status_june23_sc, n_sample) %>% 
  separate_rows(who_condition_ids, sep = "; ") %>% 
  right_join(who, by = c("who_condition_ids" = "ID")) %>% 
  filter(!is.na(level_three) & is.na(level_four)) %>% 
  group_by(level_two, level_three, relative_both_dalys) %>% 
  summarise(
    sample_size = sum(n_sample),
    n_complete_enroll = sum(str_detect(status_june23_sc, "C|E|R"), na.rm = T),
    p_complete_enroll = mean(str_detect(status_june23_sc, "C|E|R"), na.rm = T)
  ) %>% 
  mutate(complete_enroll = case_when(
    is.na(p_complete_enroll) | is.nan(p_complete_enroll)  ~ NA_character_,
    p_complete_enroll > 0.5 ~ ">50%",
    p_complete_enroll < 0.25 ~ "0-25%",
    T ~ "25-50%"
  )) %>%
  mutate(complete_enroll = factor(complete_enroll)) %>% 
  ungroup()
```


Plot.

```{r}
# Plot
treemaps %>%
  mutate_at(vars(sample_size), na_if, 0) %>% 
  ggplot(aes(
    area = relative_both_dalys, 
    fill = sample_size,
    label = level_three,
    subgroup = level_two,
  ), color = "white") +
  geom_treemap(color = "white", size = 1, alpha = 0.85) +
  geom_treemap_text(
    aes(color = complete_enroll),
    place = "centre", 
    grow = T, 
    reflow = T, 
    min.size = 1,
    padding.x = unit(2, units = "mm"),
    padding.y = unit(2, units = "mm"),
    show.legend = T
  ) +
  geom_treemap_subgroup_border(color = "white", size = 5) +
  theme(
    legend.title = element_text(vjust = 2)
  ) +
  scale_color_manual(
    values = c("#5E4FA2", "#66C2A5"),
    guide = guide_legend(override.aes = list(size = 3)),
    name = "Complete or recruiting",
    na.value = "grey70"
  ) +
  scale_fill_gradient(
    low = "#F2DF91",
    high = "#CE0A04",
    na.value = "grey90",
    name = "Total sample",
    labels = scales::comma
  )

# Save
ggsave("../../output/figure_output/figures_treemap_level_three.jpg")
```


***


# Maps

## Participants

Create data.

```{r}
# Get map
heat_map <- 
  trials %>% 
  select(nct_id, region = country_participants, n_sample) %>% 
  separate_rows(region, sep = "; ") %>% 
  group_by(region) %>% 
  summarise(sample_size = sum(n_sample, na.rm = T)) %>% 
  full_join(ggplot2::map_data('world'))
```


Identify non-matched regions.

```{r}
heat_map %>% 
  filter(is.na(long)) %>% 
  select(region, sample_size) %>% 
  sable()
```

Calculate country centroids. X = long, Y = lat.

```{r}
# Extract world data
world <- rnaturalearth::ne_countries(scale = "medium", returnclass = "sf")

# Calculate centroids
world_centroids <- 
  world %>% 
  cbind(sf::st_coordinates(sf::st_centroid(world$geometry))) %>% 
  as_tibble %>% 
  select(centroid_long = X, centroid_lat = Y, region = name)

# Harmonize this map with the previous map
world_centroids %<>% 
  filter(region != "Hong Kong") %>% 
  mutate_at(vars(region), str_replace, "United Kingdom", "UK") %>%
  mutate_at(vars(region), str_replace, "United States", "USA") %>%
  mutate_at(vars(region), str_replace, "^Korea$", "South Korea") %>%
  mutate_at(vars(region), str_replace, "^Czech.*", "Czech Republic") %>%
  mutate_at(vars(region), str_replace, "^Congo$", "Democratic Republic of the Congo") %>%
  mutate_at(vars(region), str_replace, "Lao PDR", "Laos") %>%
  mutate_at(vars(region), str_replace, "Dem.*Korea", "North Korea")

# Retain centroids of countries with data
world_centroids %<>% 
  left_join(heat_map) %>% 
  filter(!is.na(sample_size)) %>% 
  distinct(centroid_long, centroid_lat, region)
```


```{r}
country_centroids <- 
  read_csv("../../data/external_data/countries.csv") %>% 
  rename(region = name) %>% 
  filter(region != "Hong Kong") %>% 
  mutate_at(vars(region), str_replace, "United Kingdom", "UK") %>%
  mutate_at(vars(region), str_replace, "United States", "USA") %>%
  mutate_at(vars(region), str_replace, "^Korea$", "South Korea") %>%
  mutate_at(vars(region), str_replace, "^Congo \\[DRC\\]$", "Democratic Republic of the Congo") %>%
  mutate_at(vars(region), str_replace, "^Macedonia.*", "Macedonia") %>% 
  left_join(heat_map) %>% 
  filter(!is.na(sample_size)) %>% 
  distinct(longitude, latitude, region)
```


```{r}
# a <- maps::map.text("world")
# head(a)
# maps:::centroid.polygon
```


Plot.

```{r}
# Plot
heat_map %>%
  drop_na(long) %>%
  filter(region != "Antarctica") %>%
  ggplot(aes(x = long, y = lat)) +
  geom_polygon(aes(group = group, fill = sample_size), alpha = 0.9) +
  # geom_text(
  #   data = world_centroids, 
  #   aes(x = centroid_long, y = centroid_lat, label = region),
  #   size = 1
  # ) +
  geom_text(
    data = country_centroids,
    aes(x = longitude, y = latitude, label = region),
    size = 1
  ) +
  # geom_text_repel(
  #   data = country_centroids,force = 0.01,
  #   segment.size = 0.1,
  #   segment.color = "grey60",
  #   aes(x = longitude, y = latitude, label = region),
  #   size = 1
  # ) +
  theme(
    text = element_text(color = "grey20"),
    plot.subtitle = element_text(size = 14),
    axis.ticks = element_blank(),
    axis.text.x  = element_blank(),
    axis.text.y  = element_blank(),
    panel.grid = element_blank(),
    panel.background  = element_rect(fill = "white"),
    plot.background   = element_rect(fill = "white"),
    legend.position   = c(0.15, 0.2),
    legend.background = element_blank(),
    legend.key = element_blank()
  ) +
  labs(x = NULL, y = NULL) +
  ggtitle("Countries of study participants") +
  scale_fill_gradient(
    low = "#F2DF91",
    high = "#CE0A04",
    na.value = "grey90",
    name = "Total sample",
    labels = scales::comma
  ) +
  # scale_fill_distiller(
  #   palette = "Spectral",  # BuPu
  #   direction = 1,
  #   name = "Total sample",
  #   labels = scales::comma
  # ) +
  # scale_fill_gradientn(
  #   colors = rev(heat.colors(10, alpha = 0.7)),
  #   name = "Total sample",
  #   labels = scales::comma
  # ) +
  theme(legend.title = element_text(vjust = 2))

# Save
ggsave(
  "../../output/figure_output/figures_heat-map_participants.jpg",
  width = 12,
  height = 6
  )
```


## Investigators

Create data.

```{r}
# Get map
heat_map <- 
  trials %>% 
  select(nct_id, region = country_investigators, n_sample) %>% 
  separate_rows(region, sep = "; ") %>% 
  group_by(region) %>% 
  summarise(sample_size = sum(n_sample, na.rm = T)) %>% 
  full_join(ggplot2::map_data('world'))
```


Identify non-matched regions.

```{r}
heat_map %>% 
  filter(is.na(long)) %>% 
  select(region, sample_size) %>% 
  sable()
```


```{r}
country_centroids <- 
  read_csv("../../data/external_data/countries.csv") %>% 
  rename(region = name) %>% 
  filter(region != "Hong Kong") %>% 
  mutate_at(vars(region), str_replace, "United Kingdom", "UK") %>%
  mutate_at(vars(region), str_replace, "United States", "USA") %>%
  mutate_at(vars(region), str_replace, "^Korea$", "South Korea") %>%
  mutate_at(vars(region), str_replace, "^Congo \\[DRC\\]$", "Democratic Republic of the Congo") %>%
  mutate_at(vars(region), str_replace, "^Macedonia.*", "Macedonia") %>% 
  left_join(heat_map) %>% 
  filter(!is.na(sample_size)) %>% 
  distinct(longitude, latitude, region)
```


Plot.

```{r}
# Plot
heat_map %>%
  drop_na(long) %>%
  filter(region != "Antarctica") %>%
  ggplot(aes(x = long, y = lat)) +
  geom_polygon(aes(group = group, fill = sample_size), alpha = 0.9) +
  # geom_text(
  #   data = world_centroids, 
  #   aes(x = centroid_long, y = centroid_lat, label = region),
  #   size = 1
  # ) +
  geom_text(
    data = country_centroids, 
    aes(x = longitude, y = latitude, label = region),
    size = 1
  ) +
  theme(
    text = element_text(color = "grey20"),
    plot.subtitle = element_text(size = 14),
    axis.ticks = element_blank(),
    axis.text.x  = element_blank(),
    axis.text.y  = element_blank(),
    panel.grid = element_blank(),
    panel.background  = element_rect(fill = "white"),
    plot.background   = element_rect(fill = "white"),
    legend.position   = c(0.15, 0.2),
    legend.background = element_blank(),
    legend.key = element_blank()
  ) +
  labs(x = NULL, y = NULL) +
  ggtitle("Countries of study investigators") +
  scale_fill_gradient(
    low = "#F2DF91",
    high = "#CE0A04",
    na.value = "grey90",
    name = "Total sample",
    labels = scales::comma
  ) +
  # scale_fill_distiller(
  #   palette = "Spectral",  # BuPu
  #   direction = 1,
  #   name = "Total sample",
  #   labels = scales::comma
  # ) +
  # scale_fill_gradientn(
  #   colors = rev(heat.colors(10, alpha = 0.7)),
  #   name = "Total sample",
  #   labels = scales::comma
  # ) +
  theme(legend.title = element_text(vjust = 2))

# Save
ggsave("../../output/figure_output/figures_heat-map_investigators.jpg")
```


***


# Tables

## Investigators vs. Participants

Combinations of country investigators and participants with at least 5 studies.

```{r}
# Create table
investigators_vs_participants <- 
  trials %>% 
  select(nct_id, starts_with("country"), n_sample) %>% 
  separate_rows(country_investigators, sep = "; ") %>% 
  separate_rows(country_participants, sep = "; ") %>%
  group_by(country_investigators, country_participants) %>% 
  summarise(studies_n = n(), size_n = sum(n_sample)) %>%
  ungroup() %>% 
  mutate(studies_prop = scales::percent(studies_n / sum(studies_n), 0.1)) %>% 
  mutate(size_prop = scales::percent(size_n / sum(size_n, na.rm = T), 0.1)) %>%
  filter(studies_n >= 5) %>% 
  select(starts_with("loc"), starts_with("studies"), starts_with("size")) %>% 
  arrange(desc(studies_n)) %>%
  mutate_if(is.numeric, scales::comma, accuracy = 1) %>% 
  mutate_all(replace_na, "(Missing)")

# Save
write_csv(
  investigators_vs_participants,
  "../../output/table_output/figures_investigators-vs-participants.csv"
)

# Print
investigators_vs_participants %>% sable()
```



***


# Documentation {.tabset}

## Session Info

```{r session_info, echo=FALSE}
print(sessionInfo(), locale = F)
```


## References

```{r refs, echo=FALSE}
(.packages()) %>% sort %>% lapply(citation) %>% lapply(c) %>% unique
```
