---
title: 'Pediatric clinical trials: Treemaps'
author: "Stylianos Serghiou"
date: '`r format(Sys.time(), "%d/%m/%Y")`'
output:
  prettydoc::html_pretty:
    # no code_folding available
    theme: hpstr      # or: architect; https://github.com/yixuan/prettydoc
    highlight: github # or: vignette
    toc: TRUE         # no toc_float available
    df_print: kable   # obviates %>% kable; does not replace styling though
  tufte::tufte_handout: default
  pdf_document:
    highlight: tango
    df_print: kable
    latex_engine: pdflatex
    keep_tex: yes
  rmdformats::readthedown:
    highlight: kate
    df_print: kable    # obviates %>% kable; does not replace styling though
    code_folding: hide # or: show; (comment out to not give option)
  tufte::tufte_html: 
    toc: TRUE
  epuRate::epurate:
    df_print: kable
    toc: yes
  html_document:
    highlight: tango
    theme: sandstone
    df_print: kable
    toc: yes
    toc_depth: 2
    toc_float: yes
    css: "path_to_custom.css"
header-includes:
- \DeclareUnicodeCharacter{3B8}{~}
- \DeclareUnicodeCharacter{3B1}{~}
- \DeclareUnicodeCharacter{3B2}{~}
- \DeclareUnicodeCharacter{223C}{~}
- \DeclareUnicodeCharacter{2264}{~}
- \DeclareUnicodeCharacter{2265}{~}
- \DeclareUnicodeCharacter{2581}{~}
- \DeclareUnicodeCharacter{2582}{~}
- \DeclareUnicodeCharacter{2583}{~}
- \DeclareUnicodeCharacter{2585}{~}
- \DeclareUnicodeCharacter{2586}{~}
- \DeclareUnicodeCharacter{2587}{~} 
- \DeclareUnicodeCharacter{FB00}{~} 
- \usepackage{graphicx}
editor_options: 
  chunk_output_type: inline
---

<style>
p {

text-align: justify;
text-justify: interword;
padding: 0 0 0.5em 0

}
</style>

```{r setup, include=FALSE}
# Load packages
library(knitr)
library(rmdformats)
library(kableExtra)
library(ggplot2)
library(magrittr)



######### knitr

# Define chunk options
opts_chunk$set(
  echo = T,
  cache = F,  # if TRUE, no need to rerun chunks
  # cache.lazy = TRUE,  # use with big objects (>1 GB)
  cache.comments = F,  # do not rebuild if comments change
  tidy = F,  # can play with this
  warning = F, 
  message = F,
  comment = NA,
  fig.align = "center",
  fig.width = 7,
  # fig.path = "Figs/",  # export all figures to dir Figs
  linewidth = 91,
  width = 75
)


# Initiatialize hook
hook_output = knit_hooks$get("output")


# Hook to wrap output text when it exceeds 'n' using linewidth
knit_hooks$set(output = function(x, options) {
  
  if (!is.null(n <- options$linewidth)) {
    x = knitr:::split_lines(x)
    
    # wrap lines wider than 'n' 
    if (any(nchar(x) > n)) 
      x <- strwrap(x, width = n)
      x <- paste(x, collapse = "\n")
  }
  hook_output(x, options)
})


# Times a chunk and prints the time it took to run it under the chunk
# To time a chunk, include in the chunk options: {r my_chunk, timeit=TRUE}
knitr::knit_hooks$set(timeit = local({
  now = NULL
  function(before, options) {
    if (before) {
      now <<- Sys.time()
    } else {
      res = difftime(Sys.time(), now)
      now <<- NULL
      # use options$label if you want the chunk label as well
      paste('Time for this code chunk:', as.character(res))
    }
  }})
)


# For more knitr options visit: https://yihui.name/knitr/options/
# and his github page: https://github.com/yihui/knitr-examples



######### kableExtra

options(knitr.kable.NA = ''  # replace NAs in tables with blank
        , digits = 3)          # round digits (doesn't work without this here!)

## Example use
# data.frame(x = c(1,2,3), y = c(4,5,6), z = c(7,8,9)) %>% 
#   kable(booktabs = T) %>% kable_styling()

# Function to simplify table styling
sable <- function(tab, escape = T, full_width = F, drop = F, font_size = 12) {
  if (drop) {
    tab %>%
      kable(escape = escape, booktabs = T) %>%
      collapse_rows(valign = "top") %>% 
      kable_styling("striped", 
                    position = "center", 
                    full_width = full_width, 
                    font_size = font_size)
  } else {
    tab %>%
      kable(escape = escape, booktabs = T) %>%
      kable_styling("striped", 
                    position = "center", 
                    full_width = full_width,
                    font_size = font_size)
  }
}

## Guidelines
# No longer need to define options(knitr.table.format = "html"). It is now automatically done as soon as you load kableExtra
# No need to run kable() every time - done automatically as soon as you load kableExtra
# Loading kableExtra nullifies any styling applied by df_table: kable in the preamble - if you are content with standard formatting, DO NOT load kableExtra



#########  ggplot2

# Set up preferred theme in ggplot2
my_theme <- 
  # this and theme_minimal() are my favorite
  theme_light() +  
  theme(
    axis.ticks = element_blank(),
    axis.title = element_text(face = "bold"),
    axis.text.x = element_text(margin = margin(t = 3)),
    axis.text.y  = element_text(margin = margin(r = 3)),
    legend.key = element_rect(colour = NA, fill = NA),  # Avoid borders
    panel.border = element_blank(), 
    text = element_text(color = "grey20"),
    title = element_text(face = "bold")
  )

# Make the above theme the default theme
original_theme <- theme_set(my_theme)

# Use ggsave to save plots after plotting - this reduces size dramatically



######### Live preview

# Preview the HTML without having to re-knit
# https://www.r-bloggers.com/create-r-markdown-reports-and-presentations-even-better-with-these-3-practical-tips/amp/

# xaringan::infinite_moon_reader()




######### Tabbed sections

# You can organize content using tabs by applying the .tabset class attribute to headers within a document. This will cause all sub-headers of the header with the .tabset attribute to appear within tabs rather than as standalone sections. For example:

## Quarterly Results {.tabset}

### By Product



######### Update package

# To update the package use:
# Replace ~/serghiouTemplates/inst/rmarkdown/templates/report/skeleton.rmd
# library(devtools); setwd("/Users/Stelios/"); install("serghiouTemplates")
```


# Setup {.tabset}

<!-- Chunk called setup_2 to avoid running it automatically -->

```{r setup_2}
# Load packages
library(magrittr)
library(tidyverse)
library(treemapify)


# Import data
trials <- read_csv(
  "../../data/tidy_data/trials-ihme.csv"
)

ihme <- read_csv(
  "../../data/tidy_data/ihme.csv", 
  col_types = cols(ihme_id = col_character(), who_id = col_character())
)

who <- read_csv(
  "../../data/tidy_data/who.csv", 
  col_types = cols(ID = col_character())
)
```


***


# Eligibility

Number of eligible trials with categorizable conditions.

```{r}
trials %>% 
  count(is_eligible, is_classified, sort = T) %>% 
  sable()
```


***


# Level three

## Create dataset

Join with DALYs.

```{r}
# Only maintain up to level_four
treemaps <- 
  trials %>% 
  filter(is_eligible, is_classified) %>%
  select(nct_id, ihme_level_three, starts_with("n_"), status_june23_sc) %>%
  separate_rows(ihme_level_three, sep = "; ") %>%
  right_join(ihme, by = c("ihme_level_three" = "ihme_id")) %>%
  filter(level == "level_three") %>% 
  mutate(level_three = condition) %>% 
  left_join(select(who, ID, level_two), by = c("who_id" = "ID")) %>% 
  mutate(n_sample_adjust = n_sample / n_level_three)

# Remaining trials
sprintf("Number of remaining trials = %s", n_distinct(treemaps$nct_id))
```


Identify complete or active.

```{r}
# Create dataset
treemaps %<>%
  group_by(level_two, level_three, dalys) %>% 
  summarise(
    sample_size = sum(n_sample_adjust, na.rm = T),
    n_studies = sum(!is.na(n_sample)),
    n_complete_only = sum(str_detect(status_june23_sc, "C"), na.rm = T),
    n_complete_enroll = sum(str_detect(status_june23_sc, "C|E|R"), na.rm = T),
    p_complete_enroll = mean(str_detect(status_june23_sc, "C|E|R"), na.rm = T)
  ) %>% 
  mutate(complete_enroll = case_when(
    is.na(p_complete_enroll) | is.nan(p_complete_enroll)  ~ NA_character_,
    p_complete_enroll > 0.5 ~ ">50%",
    p_complete_enroll < 0.25 ~ "0-25%",
    T ~ "25-50%"
  )) %>%
  mutate(complete_enroll = factor(complete_enroll)) %>%
  mutate(complete_enroll = fct_relevel(complete_enroll, ">50%", "25-50%")) %>%
  ungroup()

# Glimpse
glimpse(treemaps)
```


Count those that have completed enrolling or are actively enrolling.

```{r}
treemaps %>%
  count(complete_enroll) %>% 
  sable()
```

Inspect levels with 0-50% enrollment.

```{r}
treemaps %>% 
  filter(complete_enroll %in% c("25-50%", "0-25%")) %>% 
  select(3:9) %>%
  arrange(complete_enroll) %>% 
  sable()
```


## Plot

```{r}
# Create palette
colfunc <- colorRampPalette(c("red", "yellow", "green"))

# Plot
treemaps %>%
  mutate_at(vars(sample_size), na_if, 0) %>% 
  ggplot(aes(
    area = dalys, 
    fill = sample_size,
    label = level_three,
    subgroup = level_two,
  ), color = "white") +
  geom_treemap(color = "white", size = 1) +
  geom_treemap_text(
    colour = "grey20", 
    place = "centre", 
    grow = F, 
    reflow = T, 
    min.size = 1,
    padding.x = unit(2, units = "mm"),
    padding.y = unit(2, units = "mm"),
  ) +
  geom_treemap_subgroup_border(color = "white", size = 5) +
  labs(fill = "Total sample") +
  theme(legend.title = element_text(vjust = 2)) +
  scale_fill_gradient(
    low = "#F2DF91",
    high = "#CE0A04",
    na.value = "grey90",
    name = "Total sample",
    labels = scales::comma
  )
  # scale_fill_gradientn(
  #   labels = scales::comma,
  #   colours = heat.colors(10, alpha = 0.65),
  #   na.value = "grey50"
  # )
  # scale_fill_distiller(palette = "Greens")
  # scale_fill_distiller(palette = "Spectral")
  # scale_fill_gradientn(colours = alpha(colfunc(10), 0.7))
  # scale_fill_viridis_c(option = "B")
  # scale_fill_gradient(low = "yellow", high = "red", na.value = "grey")
  
# Save
ggsave("../../output/figure_output/treemaps_level-three.jpg")
```


## Plot - Enrollment

```{r}
# Create palette
colfunc <- colorRampPalette(c("red", "yellow", "green"))

# Plot
treemaps %>%
  mutate_at(vars(sample_size), na_if, 0) %>% 
  ggplot(aes(
    area = dalys, 
    fill = sample_size,
    label = level_three,
    subgroup = level_two,
  ), color = "white") +
  geom_treemap(color = "white", size = 1) +
  geom_treemap_text(
    aes(color = complete_enroll),
    place = "centre", 
    grow = F,
    reflow = T, 
    min.size = 1,
    padding.x = unit(2, units = "mm"),
    padding.y = unit(2, units = "mm"),
    show.legend = T
  ) +
  geom_treemap_subgroup_border(color = "white", size = 5) +
  labs(color = "Complete or recruiting") +
  guides(color = guide_legend(override.aes = list(size = 3))) +
  theme(
    legend.title = element_text(vjust = 2)
  ) +
  scale_fill_gradient(
    low = "#F2DF91",
    high = "#CE0A04",
    na.value = "grey90",
    name = "Total sample",
    labels = scales::comma
  ) +
  scale_color_brewer(palette = "Spectral") +
  scale_color_manual(
    values = c("grey20", "dodgerblue3", "coral3"),
    na.value = "white",
    name = "Complete or recruiting"
  )
  # scale_fill_gradientn(
  #   labels = scales::comma,
  #   colours = heat.colors(10, alpha = 0.65),
  #   na.value = "grey50"
  # )
  # scale_fill_distiller(palette = "Greens")
  # scale_fill_distiller(palette = "Spectral")
  # scale_fill_gradientn(colours = alpha(colfunc(10), 0.7))
  # scale_fill_viridis_c(option = "B")
  # scale_fill_gradient(low = "yellow", high = "red", na.value = "grey")
  
# Save
ggsave("../../output/figure_output/treemaps_level-three_enrollment_chosen.jpg")
```


## Plot - Completed

```{r}
# Create palette
colfunc <- colorRampPalette(c("red", "yellow", "green"))

# Plot
treemaps %>%
  mutate(sample_size = if_else(n_complete_only > 0, sample_size, 0)) %>% 
  mutate_at(vars(sample_size), na_if, 0) %>% 
  ggplot(aes(
    area = dalys, 
    fill = sample_size,
    label = level_three,
    subgroup = level_two,
  ), color = "white") +
  geom_treemap(color = "white", size = 1) +
  geom_treemap_text(
    colour = "grey20", 
    place = "centre", 
    grow = F, 
    reflow = T, 
    min.size = 1,
    padding.x = unit(2, units = "mm"),
    padding.y = unit(2, units = "mm"),
  ) +
  geom_treemap_subgroup_border(color = "white", size = 5) +
  labs(fill = "Total sample") +
  theme(legend.title = element_text(vjust = 2)) +
  scale_fill_gradient(
    low = "#F2DF91",
    high = "#CE0A04",
    na.value = "grey90",
    name = "Total sample",
    labels = scales::comma
  )
  # scale_fill_gradientn(
  #   labels = scales::comma,
  #   colours = heat.colors(10, alpha = 0.65),
  #   na.value = "grey50"
  # )
  # scale_fill_distiller(palette = "Greens")
  # scale_fill_distiller(palette = "Spectral")
  # scale_fill_gradientn(colours = alpha(colfunc(10), 0.7))
  # scale_fill_viridis_c(option = "B")
  # scale_fill_gradient(low = "yellow", high = "red", na.value = "grey")
  
# Save
ggsave("../../output/figure_output/treemaps_level-three_completed_chosen.jpg")
```

***


# Level four

## Create dataset

Join with DALYs.

```{r}
# Only maintain up to level_four
treemaps <- 
  trials %>% 
  filter(is_eligible, is_classified) %>%
  select(nct_id, ihme_level_four, starts_with("n_"), status_june23_sc) %>%
  separate_rows(ihme_level_four, sep = "; ") %>%
  right_join(ihme, by = c("ihme_level_four" = "ihme_id")) %>%
  filter(level == "level_four") %>% 
  mutate(level_four = condition) %>% 
  left_join(select(who, -level_four), by = c("who_id" = "ID")) %>% 
  mutate(n_sample_adjust = n_sample / n_level_four)

# Remaining trials
sprintf("Number of remaining trials = %s", n_distinct(treemaps$nct_id))
```


Identify complete or active.

```{r}
# Create dataset
treemaps %<>%
  group_by(level_two, level_three, level_four, dalys) %>% 
  summarise(
    sample_size = sum(n_sample_adjust, na.rm = T),
    n_studies = sum(!is.na(n_sample)),
    n_complete_enroll = sum(str_detect(status_june23_sc, "C|E|R"), na.rm = T),
    p_complete_enroll = mean(str_detect(status_june23_sc, "C|E|R"), na.rm = T)
  ) %>% 
  mutate(complete_enroll = case_when(
    is.na(p_complete_enroll) | is.nan(p_complete_enroll)  ~ NA_character_,
    p_complete_enroll > 0.5 ~ ">50%",
    p_complete_enroll < 0.25 ~ "0-25%",
    T ~ "25-50%"
  )) %>%
  mutate(complete_enroll = factor(complete_enroll)) %>% 
  ungroup()

# Glimpse
glimpse(treemaps)
```


Count those that have completed enrolling or are actively enrolling.

```{r}
treemaps %>%
  count(complete_enroll) %>% 
  sable()
```

Inspect levels with 0-50% enrollment.

```{r}
treemaps %>% 
  filter(complete_enroll %in% c("25-50%", "0-25%")) %>% 
  select(3:9) %>%
  arrange(complete_enroll) %>% 
  sable()
```


## Plot

```{r}
# Create palette
colfunc <- colorRampPalette(c("red", "yellow", "green"))

# Plot
treemaps %>%
  mutate_at(vars(sample_size), na_if, 0) %>%
  drop_na(level_two, level_three) %>% 
  ggplot(aes(
    area = dalys, 
    fill = sample_size,
    label = level_four,
    subgroup = level_two,
    subgroup2 = level_three
  ), color = "white") +
  geom_treemap(color = "white", size = 1) +
  geom_treemap_text(
    colour = "grey20", 
    place = "centre", 
    grow = F, 
    reflow = T, 
    min.size = 1,
    padding.x = unit(2, units = "mm"),
    padding.y = unit(2, units = "mm"),
  ) +
  geom_treemap_subgroup_border(color = "white", size = 5) +
  geom_treemap_subgroup2_border(color = "white", size = 2) +
  labs(fill = "Total sample") +
  theme(legend.title = element_text(vjust = 2)) +
  scale_fill_gradient(
    low = "#F2DF91",
    high = "#CE0A04",
    na.value = "grey90",
    name = "Total sample",
    labels = scales::comma
  )
  # scale_fill_gradientn(
  #   labels = scales::comma,
  #   colours = heat.colors(10, alpha = 0.65),
  #   na.value = "grey50"
  # )
  # scale_fill_distiller(palette = "Greens")
  # scale_fill_distiller(palette = "Spectral")
  # scale_fill_gradientn(colours = alpha(colfunc(10), 0.7))
  # scale_fill_viridis_c(option = "B")
  # scale_fill_gradient(low = "yellow", high = "red", na.value = "grey")
  
# Save
ggsave("../../output/figure_output/treemaps_level-four.jpg")
```


## Plot - Enrollment

```{r}
# Create palette
colfunc <- colorRampPalette(c("red", "yellow", "green"))

# Plot
treemaps %>%
  mutate_at(vars(sample_size), na_if, 0) %>%
  drop_na(level_two, level_three) %>% 
  ggplot(aes(
    area = dalys, 
    fill = sample_size,
    label = level_four,
    subgroup = level_two,
    subgroup2 = level_three
  ), color = "white") +
  geom_treemap(color = "white", size = 1) +
  geom_treemap_text(
    aes(color = complete_enroll),
    place = "centre", 
    grow = F,
    reflow = T, 
    min.size = 1,
    padding.x = unit(2, units = "mm"),
    padding.y = unit(2, units = "mm"),
    show.legend = T
  ) +
  geom_treemap_subgroup_border(color = "white", size = 5) +
  geom_treemap_subgroup2_border(color = "white", size = 2) +
  labs(fill = "Total sample") +
  guides(color = guide_legend(override.aes = list(size = 3))) +
  theme(legend.title = element_text(vjust = 2)) +
  scale_fill_gradient(
    low = "#F2DF91",
    high = "#CE0A04",
    na.value = "grey90",
    name = "Total sample",
    labels = scales::comma
  ) +
  scale_color_manual(
    values = c("grey20", "dodgerblue3", "coral3"),
    na.value = "white",
    name = "Complete or recruiting"
  )
  # scale_fill_gradientn(
  #   labels = scales::comma,
  #   colours = heat.colors(10, alpha = 0.65),
  #   na.value = "grey50"
  # )
  # scale_fill_distiller(palette = "Greens")
  # scale_fill_distiller(palette = "Spectral")
  # scale_fill_gradientn(colours = alpha(colfunc(10), 0.7))
  # scale_fill_viridis_c(option = "B")
  # scale_fill_gradient(low = "yellow", high = "red", na.value = "grey")
  
# Save
ggsave("../../output/figure_output/treemaps_level-four_enrollment.jpg")
```


***


# Documentation {.tabset}

## Session Info

```{r session_info, echo=FALSE}
print(sessionInfo(), locale = F)
```


## References

```{r refs, echo=FALSE}
(.packages()) %>% sort %>% lapply(citation) %>% lapply(c) %>% unique
```
